Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-23 manuscript/main.tex
revised methods description and background

%%%  Purposes of policy measurement %%% 
The measurement task on which we are focused is the identification of comparable policy actions (e.g., adoption, consideration) across jurisdictions---US states in particular. Scholars of public policy, legislative politics, and related areas have used measurements of comparable policy actions in a variety of research tasks. These include the study of policy diffusion \citep{karch2007emerging}, the comparison of policies on a select legislative issue \citep[e.g., ][]{huber2001legislatures,mycoff2009empirical}, and influence/adoption of model legislation introduced by advocacy organizations \citep[e.g., ][]{garrett2015,burgess2016legislative}. In each of these areas of research, scholars make use of measurements of consistent policy actions across jurisdictions. Below we review a variety of methods, and conceptual definitions that researchers have used in measuring consistent policy actions.

%%% Mechanics of policy measurement %%% 
Public policy research on cross-jurisdiction comparable policy actions has conventionally involved the manual identification of related policies across states, countries or local governments in one or a handful of policy areas \citep[e.g., ][]{walker1969,berry1990,simmons2004,gilardi2009,krause2011policy}. This is a manual approach to measurement at the monadic level. In the area of policy diffusion research, recognizing the limitations of monadic levels of measurement, researchers have developed dyadic approaches to studying the diffusion relationships between states \citep{volden2006,boehmke2009}. In the most recent iteration of dyadic approaches, \cite{desmarais2015} apply network inference algorithms to US state adoption sequences in over 100 policy domains to empirically infer the underlying network through which policies diffuse. In another recent innovation in measurement for policy analysis, \cite{garrett2015} analyze the text of US state legislation to identify the influence of model legislation, as introduced by interest groups.

@@

Sequences in text that convey equivalent content matter often do not match perfectly. Formatting, white space, typographical errors, etc. would decrease the precision dramatically if only exact matches were used. The SW algorithm, therefore, returns the optimal alignment while allowing for mismatches and gaps. The extent to which such imperfections are tolerated is governed by parameters that are set by the researcher. There are three such parameters: the match score (reward for exactly matching words), the mismatch score (penalty for including words that do not match), and the gap score (penalty for including placeholder words in matching a shorter sequence to a longer sequence). The goal of the algorithm is to return the the alignment with the highest score given the input sequences and the parameters. Consider the following two excerpts from Alaska State Bill 203 (28th session) and North Carolina House Bill 366 (2015) respectively:

@@

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $124 * 10^9$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
document that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}

>>>>

%%%  Purposes of policy measurement %%% 
The measurement task on which we are focused is the identification of comparable policy actions (e.g., adoption, consideration) across jurisdictions---US states in particular. Scholars of public policy, legislative politics, and related areas have used measurements of comparable policy actions in a variety of research tasks. These include the study of policy diffusion \citep{karch2007emerging}, the comparison of policies on a select legislative issue \citep[e.g., ][]{huber2001legislatures,mycoff2009empirical}, and influence/adoption of model legislation introduced by advocacy organizations \citep[e.g., ][]{garrett2015,burgess2016legislative}. In each of these areas of research, scholars make use of measurements of consistent policy actions across jurisdictions. Below we review a variety of methods, and conceptual definitions that researchers have used in identifying similar policy actions.

%%% Mechanics of policy measurement %%% 
We first consider the levels at which measurement has been conducted in past work. Public policy research on cross-jurisdiction comparable policy actions has conventionally involved the manual identification of related policies across states, countries or local governments in one or a handful of policy areas \citep[e.g., ][]{walker1969,berry1990,simmons2004,gilardi2009,krause2011policy}. This is a manual approach to measurement at the monadic (i.e., governing jurisdiction) level. Recognizing the limitations of monadic levels of measurement, researchers have developed dyadic approaches to studying the diffusion relationships between states \citep{volden2006,boehmke2009}. In the most recent iteration of dyadic approaches, \cite{desmarais2015} apply network inference algorithms to US state adoption sequences in over 100 policy domains to empirically infer the underlying network through which policies diffuse. In another recent innovation in measurement for policy analysis, \cite{garrett2015} analyze the text of US state legislation through pairwise comparison with model legislation introduced by interest groups to identify the influence of model legislation.

@@

Sequences in text that convey similar---even equivalent---policy content often do not match perfectly. Formatting, white space, typographical errors, etc. would decrease the precision dramatically if only exact matches were used. The SW algorithm, therefore, returns the optimal alignment while allowing for mismatches and gaps. The extent to which such imperfections are tolerated is governed by parameters that are set by the researcher. There are three such parameters: the match score (reward for exactly matching words), the mismatch score (penalty for including words that do not match), and the gap score (penalty for including placeholder words in matching a shorter sequence to a longer sequence). The goal of the algorithm is to return the the alignment with the highest score given the input sequences and the parameters. Consider the following two excerpts from Alaska State Bill 203 (28th session) and North Carolina House Bill 366 (2015) respectively:

@@

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $124 * 10^9$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
documents that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}
